---
title: "MRP"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rstanarm)
library(ggplot2)
library(bayesplot)
library(dplyr)
library(tidyr)
library(plyr)
library(tibble)
```

```{r example data gen}
## Used for generating random data in MRP example

if (!exists('mrp_sim')){ ## Defining function skipped if already defined

  simulate_mrp_data <- function(n) {
  J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) # Columns of post-strat matrix, plus one for size
  colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
  count <- 0
  for (i1 in 1:J[1]){
    for (i2 in 1:J[2]){
      for (i3 in 1:J[3]){
        for (i4 in 1:J[4]){
          for (i5 in 1:J[5]){
              count <- count + 1
              # Fill them in so we know what category we are referring to
              poststrat[count, 1:5] <- c(i1-1, i2, i3,i4,i5) 
          }
        }
      }
    }
  }
  # Proportion in each sample in the population
  p_male <- c(0.52, 0.48)
  p_eth <- c(0.5, 0.2, 0.3)
  p_age <- c(0.2,.1,0.2,0.2, 0.10, 0.1, 0.1)
  p_income<-c(.50,.35,.15)
  p_state_tmp<-runif(50,10,20)
  p_state<-p_state_tmp/sum(p_state_tmp)
  poststrat$N<-0
  for (j in 1:prod(J)){
    poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
      p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) #Adjust the N to be the number observed in each category in each group
  }
  
  # Now let's adjust for the probability of response
  p_response_baseline <- 0.01
  p_response_male <- c(2, 0.8) / 2.8
  p_response_eth <- c(1, 1.2, 2.5) / 4.7
  p_response_age <- c(1, 0.4, 1, 1.5,  3, 5, 7) / 18.9
  p_response_inc <- c(1, 0.9, 0.8) / 2.7
  p_response_state <- rbeta(50, 1, 1)
  p_response_state <- p_response_state / sum(p_response_state)
  p_response <- rep(NA, prod(J))
  for (j in 1:prod(J)) {
    p_response[j] <-
      p_response_baseline * p_response_male[poststrat[j, 1] + 1] *
      p_response_eth[poststrat[j, 2]] * p_response_age[poststrat[j, 3]] *
      p_response_inc[poststrat[j, 4]] * p_response_state[poststrat[j, 5]]
  }
  people <- sample(prod(J), n, replace = TRUE, prob = poststrat$N * p_response)
  
  ## For respondent i, people[i] is that person's poststrat cell,
  ## some number between 1 and 32
  n_cell <- rep(NA, prod(J))
  for (j in 1:prod(J)) {
    n_cell[j] <- sum(people == j)
  }
  
  coef_male <- c(0,-0.3)
  coef_eth <- c(0, 0.6, 0.9)
  coef_age <- c(0,-0.2,-0.3, 0.4, 0.5, 0.7, 0.8, 0.9)
  coef_income <- c(0,-0.2, 0.6)
  coef_state <- c(0, round(rnorm(49, 0, 1), 1))
  coef_age_male <- t(cbind(c(0, .1, .23, .3, .43, .5, .6),
                           c(0, -.1, -.23, -.5, -.43, -.5, -.6)))
  true_popn <- data.frame(poststrat[, 1:5], cat_pref = rep(NA, prod(J)))
  for (j in 1:prod(J)) {
    true_popn$cat_pref[j] <- plogis(
      coef_male[poststrat[j, 1] + 1] +
        coef_eth[poststrat[j, 2]] + coef_age[poststrat[j, 3]] +
        coef_income[poststrat[j, 4]] + coef_state[poststrat[j, 5]] +
        coef_age_male[poststrat[j, 1] + 1, poststrat[j, 3]]
      )
  }
  
  #male or not, eth, age, income level, state, city
  y <- rbinom(n, 1, true_popn$cat_pref[people])
  male <- poststrat[people, 1]
  eth <- poststrat[people, 2]
  age <- poststrat[people, 3]
  income <- poststrat[people, 4]
  state <- poststrat[people, 5]
  
  sample <- data.frame(cat_pref = y, 
                       male, age, eth, income, state, 
                       id = 1:length(people))
  
  #Make all numeric:
  for (i in 1:ncol(poststrat)) {
    poststrat[, i] <- as.numeric(poststrat[, i])
  }
  for (i in 1:ncol(true_popn)) {
    true_popn[, i] <- as.numeric(true_popn[, i])
  }
  for (i in 1:ncol(sample)) {
    sample[, i] <- as.numeric(sample[, i])
  }
  list(
    sample = sample,
    poststrat = poststrat,
    true_popn = true_popn
  )
}
## define function data points, print
mrp_sim <- simulate_mrp_data(n=1200)
str(mrp_sim)
}
```
```{R Census prep}
census <- read.csv("C:/Users/Julius/Downloads/Census_useful/2016Census_G01_AUS_CED.csv", header = TRUE)
census1 <- census[order(census$CED_CODE_2016),]
proper_names <- read.csv("C:/Users/Julius/Downloads/Census_useful/CED_DivisionNms.csv", header = TRUE)
proper_names <- proper_names[order(proper_names$Ced.Code16),] ## sorting variables
census2 <- subset(census1, select= -c(CED_CODE_2016)) ## drop useless CED code
names <- subset(proper_names, select = c(Ced.Name)) ## get electorate name
census_final <- cbind(names,census2) ## join electorate name to DF
census_final <- census_final[order(census_final$Ced.Name),] ## electorates in alphabetical order
```

```{R 2016 election prep}

## Creating Data frame with ALP 2016 votes and total votes(use this to decrease the total number of people in an electorate?)

tpp2016 <- read.csv("C:/Users/Julius/Downloads/Aus_Elections/HouseTppByDivisionDownload-20499.csv") ## Two Party pref, so even with Labor/Lib dead last should still give data for those two

votes <- tpp2016$Australian.Labor.Party.Votes / tpp2016$TotalVotes ## ALP TPP
```
Problem: Facing significant issue here with the census data, not really compatible with how it was set up in the example. 
Sample data in the example is essentially a series of various variables associated with an outcome and whether they liked cats, as compared to census data which is all actual info.

Solution: Transform everything into percentages.

What matters when deciding a vote? Age, Religion, Education, Xenophobia, Gender
 
Age -> Various age groups -> Age_0_4_yr_M Age_5_14_yr_M Age_15_19_yr_M Age_20_24_yr_M Age_25_34_yr_M Age_35_44_yr_M Age_45_54_yr_M Age_55_64_yr_M Age_65_74_yr_M Age_75_84_yr_M Age_85ov_M
Xeno -> Age groups + English only in home + indigenous persons + Born in Aus (Assimilation Metric has to be programmed in) -> (Age bins) + Lang_spoken_home_Eng_only_M + Indigenous_P_Tot_M + Birthplace_Australia_M
Education -> Education groups -> Create bins for completed / undergoing VCE vs Dropped out
Gender -> Use genders bins rather than _P
Housing -> Private vs Public - Count_psns_occ_priv_dwgs_M Count_Persons_other_dwgs_M 
```{r binning}

temp <- colnames(census_final)

## VCE 
VCE_M <- rowSums(census_final[,c("High_yr_schl_comp_Yr_12_eq_M", "Age_psns_att_edu_inst_25_ov_M", "Age_psns_att_edu_inst_20_24_M","Age_psns_att_edu_inst_15_19_M", "Age_psns_att_educ_inst_5_14_M", "Age_psns_att_educ_inst_0_4_M")])

VCE_F <- rowSums(census_final[,c("High_yr_schl_comp_Yr_12_eq_F", "Age_psns_att_edu_inst_25_ov_F", "Age_psns_att_edu_inst_20_24_F","Age_psns_att_edu_inst_15_19_F", "Age_psns_att_educ_inst_5_14_F", "Age_psns_att_educ_inst_0_4_F")])

##non VCE

Un_M <- rowSums(census_final[,c("High_yr_schl_comp_Yr_11_eq_M", "High_yr_schl_comp_Yr_10_eq_M", "High_yr_schl_comp_Yr_9_eq_M","High_yr_schl_comp_Yr_8_belw_M", "High_yr_schl_comp_D_n_g_sch_M")])

Un_F <- rowSums(census_final[,c("High_yr_schl_comp_Yr_11_eq_F", "High_yr_schl_comp_Yr_10_eq_F", "High_yr_schl_comp_Yr_9_eq_F","High_yr_schl_comp_Yr_8_belw_F", "High_yr_schl_comp_D_n_g_sch_F")])

Census_manip <- subset(census_final, select= -c(High_yr_schl_comp_Yr_11_eq_M,High_yr_schl_comp_Yr_10_eq_M,High_yr_schl_comp_Yr_9_eq_M,High_yr_schl_comp_Yr_8_belw_M,High_yr_schl_comp_D_n_g_sch_M,High_yr_schl_comp_Yr_11_eq_F,High_yr_schl_comp_Yr_10_eq_F,High_yr_schl_comp_Yr_9_eq_F,High_yr_schl_comp_Yr_8_belw_F,High_yr_schl_comp_D_n_g_sch_F,High_yr_schl_comp_Yr_12_eq_M, Age_psns_att_edu_inst_25_ov_M, Age_psns_att_edu_inst_20_24_M,Age_psns_att_edu_inst_15_19_M, Age_psns_att_educ_inst_5_14_M, Age_psns_att_educ_inst_0_4_M,High_yr_schl_comp_Yr_12_eq_F, Age_psns_att_edu_inst_25_ov_F, Age_psns_att_edu_inst_20_24_F,Age_psns_att_edu_inst_15_19_F, Age_psns_att_educ_inst_5_14_F, Age_psns_att_educ_inst_0_4_F))

census <- cbind(Census_manip,Un_M,Un_F,VCE_M,VCE_F) ## overwriting initial census variable

## Getting every datapoint as % 
temp <- subset(census, select= c(Ced.Name)) # grab electorate name for later due to be non numeric
census <- subset(census, select= -c(Ced.Name)) # remove electorate name
census <- census / census$Tot_P_P # divide every variable by the total population to get % for each category
census <- subset(census, select= -c(Tot_P_P)) # remove useless variable
census <- cbind(census,temp) # add electorate name back in
census <- filter(census, Ced.Name %in% tpp2016$DivisionNm) ## filter census data to only be from electorates
census <- subset(census, select= -c(Ced.Name))
census <- cbind(census,votes)
```
```{r manipulation}

## clean up variable set up from earlier ## breaks initial fake data generation step
#rm(list=setdiff(ls(), "census")) ## neatly clear out all variables

## Modeling in actuality
fit <- stan_glmer(
  votes ~ factor(Un_M) +  
    (1 | Birthplace_Australia_M) + (1|Lang_spoken_home_Eng_only_M), ## include intercepts in the cells based on data we have, but are not using 
  family = gaussian, ## exponential probability, i.e no one demo will ever vote 100% one way
  data = census ## data being in the model
)

posterior_prob <- posterior_linpred(fit, transform = TRUE)

## These are the weightings, use % of votes from electorate to weigh sample
poststrat_prob <- posterior_prob %*% (census$Tot_P_M + census$Tot_P_F) / sum(census$Tot_P_M + census$Tot_P_F) 

model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
round(model_popn_pref, 3)

## filler dataframe 
state_df <- data.frame(
  State = 1:150,
  model_state_sd = rep(-1, 150),
  model_state_TPP = rep(-1, 150),
  true_state_TPP = rep(-1, 150),
  N = rep(-1, 150)
)

## generating new data for the data frame
census <- rownames_to_column(census)
rowname <- as.numeric(as.character(unlist(census[[1]])))
census <- subset(census, select = -c(rowname))
census <- cbind(census,rowname)
for(i in 1:length(levels(as.factor(census$rowname)))) {
  poststrat_state <- census[census$rowname == i, ]
    posterior_prob_state <- posterior_linpred(
    fit,
    transform = TRUE,
    draws = 1000,
    newdata = as.data.frame(poststrat_state)
  )
  poststrat_prob_state <- (posterior_prob_state %*% poststrat_state$rowname) / sum(poststrat_state$rowname)
  #This is the estimate for popn in state:
  state_df$model_state_TPP[i] <- round(mean(poststrat_prob_state), 6)
  state_df$model_state_sd[i] <- round(sd(poststrat_prob_state), 6)
  #And what is the actual popn?
  state_df$N[i] <- length(census$votes[census$state == i]) ## what does this do?
  state_df$true_state_TPP <- census$votes
  state_df$diff_in_TPP <- abs(state_df$model_state_TPP - state_df$true_state_TPP)
  }

```
