---
title: "MRP"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rstanarm)
library(ggplot2)
library(bayesplot)
library(plyr)
library(dplyr)
library(tidyr)
library(tibble)
```

```{R Census prep}
census <- read.csv("C:/Users/Julius/Downloads/Census_useful/commonwealth_electorate_data.csv", header = TRUE)
census_final <- census[order(census$Electorate),]
```

```{R 2016 election prep}

## Creating Data frame with ALP 2016 votes and total votes(use this to decrease the total number of people in an electorate?)
tpp2019 <- read.csv("C:/Users/Julius/Downloads/Aus_Elections/2019_HouseTppByDivision.csv") ## Two Party pref, so even with Labor/Lib dead last should still give data for those two

tpp2019 <- tpp2019[order(tpp2019$DivisionNm),] # make sure electorates are in correct order
votes <- tpp2019$Australian.Labor.Party.Percentage/100
swing <- tpp2019$Swing
State <- tpp2019$StateAb
rural <- read.csv("C:/Users/Julius/Downloads/Aus_Elections/demographic-classification-as-at-3-july-2020.xlsx - Australia - demographic classif.csv")
rural <- rural[order(rural$Electoral.division),]
rural <- rural$Demographic.classification
prior_tpp <- round(votes + swing/100,2) ## may need to round to 2 decimal points, could be overly specific with 3
```
```{r binning}

## binding census outcomes and votes
census <- cbind(census_final,votes,State,rural,swing,prior_tpp)

## creating rental stress and mortgage stress variables
census$Median.weekly.household.income.... <- gsub(",","",census$Median.weekly.household.income....) ## x,xxx format for numbers is preventing conversion to numeric
census$Median.monthly.mortgage.repayments.... <- gsub(",","",census$Median.monthly.mortgage.repayments....) 
census$Median.weekly.household.income.... <- as.numeric(as.character(census$Median.weekly.household.income....))
census$Median.monthly.mortgage.repayments.... <- as.numeric(as.character(census$Median.monthly.mortgage.repayments....))

census$rental_stress <- round_any(census$Median.weekly.rent..../census$Median.weekly.household.income...., 0.02)
census$mortgage_stress <- round(census$Median.monthly.mortgage.repayments..../census$Median.weekly.household.income....,1)
census$Median.weekly.household.income.... <- round_any(census$Median.weekly.household.income...., 50)
census$Born.overseas <- round(census$Born.overseas, 2)

## blue collar / white collar classes for work
census$white_collar <- round(census$Professionals + census$Clerical.and.Administrative.Workers + census$Community.and.Personal.Service.Workers,1)
census$blue_collar <- round(census$Technicians.and.Trades.Workers + census$Sales.Workers + census$Machinery.Operators.and.Drivers + census$Labourers,1) 
census$Managers <- round(census$Profession_Managers,1)

#### drop factors from census that I don't use in analysis? ####

## population density for each electorate would be really damn good
```
```{r manipulation}

## Modeling in actuality
fit <- stan_glmer(
  votes ~ factor(Median.weekly.household.income....) + factor(rental_stress) + factor(rural) + factor(Born.overseas) + factor(blue_collar) + factor(white_collar) + factor(Managers)
       + (1|State) + (1|X0.to.17.years.old) + (1|X18.to.34.years.old) + (1|X35.to.49.years.old) + (1|X50.to.64.years.old) +(1|X65.to.79.years.old) + (1|X80.years.old.and.over),
  family = gaussian, ## exponential probability, i.e no one demo will ever vote 100% one way
  data = census ## data being in the model
)

## filler dataframe 
state_df <- data.frame(electorate = rep(-1, 151))

## generating new data for the data frame
census <- rownames_to_column(census)
for(i in 1:length(levels(as.factor(census$rowname)))) {
  poststrat_state <- census[census$rowname == i, ]
    posterior_prob_state <- posterior_linpred(
    fit,
    transform = TRUE,
    draws = 4000,
    newdata = as.data.frame(poststrat_state)
  )
poststrat_prob_state <- posterior_prob_state # %*% (census_tmp$Tot_P_P) / sum(census_tmp$Tot_P_P)
  #This is the estimate for popn in state:
  state_df$model_state_sd[i] <- round(sd(poststrat_prob_state), 6)
  state_df$model_state_swing[i] <- round(mean(poststrat_prob_state), 6)
  state_df$true_state_swing <- census$votes
  state_df$diff_in_swing <- state_df$model_state_swing - state_df$true_state_swing
  state_df$electorate <- census$Electorate
  }
```

## Needed variables from files
professions - all headings align with order in census proper - 2016Census_G53B_VIC_SA1.csv 
median income - Median_tot_prsnl_inc_weekly - 2016Census_G02_VIC_SA1.csv
median rent - Median_rent_weekly - 2016Census_G02_VIC_SA1.csv
born overseas - Birthplace_Elsewhere_P  - 2016Census_G01_VIC_SA1.csv 
Age profile bins - all - 2016Census_G04A_VIC_SA1.csv + 2016Census_G04B_VIC_SA1.csv - add on to brackets in 2016Census_G01_VIC_SA1.csv
family without children - CF_no_children_P - 2016Census_G25_VIC_SA1.csv

```{r applying to Goldstein SA1s}
tmp <- read.csv("C:/Users/Julius/Downloads/Aus_Elections/Goldstein_polling_data.csv", header = TRUE) ## existing SA1 prediction data
SA1s <- unique(tmp$SA1_id) ## SA1 id's for Goldstein

## variables already have
rural <- rep('Inner Metropolitan',(length(SA1s)))
State <- rep('VIC',(length(SA1s)))

professions <- read.csv("C:/Users/Julius/Downloads/2016 Census GCP Statistical Area 1 for VIC/2016Census_G53B_VIC_SA1.csv")
mix <- read.csv("C:/Users/Julius/Downloads/2016 Census GCP Statistical Area 1 for VIC/2016Census_G01_VIC_SA1.csv")
median_rent <- read.csv("C:/Users/Julius/Downloads/2016 Census GCP Statistical Area 1 for VIC/2016Census_G02_VIC_SA1.csv")
age1 <- read.csv("C:/Users/Julius/Downloads/2016 Census GCP Statistical Area 1 for VIC/2016Census_G04A_VIC_SA1.csv")
age2 <- read.csv("C:/Users/Julius/Downloads/2016 Census GCP Statistical Area 1 for VIC/2016Census_G04B_VIC_SA1.csv")
family_wo_children <- read.csv("C:/Users/Julius/Downloads/2016 Census GCP Statistical Area 1 for VIC/2016Census_G25_VIC_SA1.csv")

age <- cbind(age1,age2) ## removing age foolishness

## filter based on SA1s in Goldstein

professions <- professions[professions$SA1_7DIGITCODE_2016 %in% SA1s ,]
mix <- mix[mix$SA1_7DIGITCODE_2016 %in% SA1s ,]
median_rent <- median_rent[median_rent$SA1_7DIGITCODE_2016 %in% SA1s,]
age <- age[age$SA1_7DIGITCODE_2016 %in% SA1s,]
family_wo_children <- family_wo_children[family_wo_children$SA1_7DIGITCODE_2016 %in% SA1s,]

## straight up extraction
Couple.family.without.children <- family_wo_children$CF_Total_P
Born.overseas <- mix$Birthplace_Elsewhere_P


## profession binning
white_collar <- professions$Tot_OcProf + professions$Tot_OcClericAdm + professions$Tot_OcComPerS
blue_collar <- professions$Tot_OcTechTrdW + professions$Tot_OcSalesWk + professions$Tot_OcMacOp_Driv +  professions$Tot_OcLab
Managers <- professions$Tot_OcMngr

## age binning
X0.to.17.years.old <- (age$Age_yr_0_4_P + age$Age_yr_5_9_P + age$Age_yr_10_14_P +age$Age_yr_15_P + age$Age_yr_16_P + age$Age_yr_17_P)
X18.to.34.years.old <- (age$Age_yr_18_P + age$Age_yr_19_P + age$Age_yr_20_24_P + age$Age_yr_25_29_P + age$Age_yr_30_34_P)
X35.to.49.years.old<- (age$Age_yr_35_39_P + age$Age_yr_40_44_P + age$Age_yr_45_49_P)
X50.to.64.years.old <- (age$Age_yr_50_54_P + age$Age_yr_55_59_P + age$Age_yr_60_64_P)
X65.to.79.years.old <- (age$Age_yr_65_69_P +age$Age_yr_70_74_P +age$Age_yr_75_79_P)
X80.years.old.and.over <- (age$Age_yr_80_84_P + age$Age_yr_85_89_P + age$Age_yr_90_94_P + age$Age_yr_95_99_P + age$Age_yr_100_yr_over_P)

## putting everything together

Gold_SA1 <- cbind(Couple.family.without.children,Born.overseas,median_rent,rural,State,white_collar,blue_collar,Managers,X0.to.17.years.old,X18.to.34.years.old,X35.to.49.years.old,X50.to.64.years.old,X65.to.79.years.old,X80.years.old.and.over)
Gold_SA1 <- as.data.frame(Gold_SA1)
write.csv(Gold_SA1, file = "C:/Users/Julius/Downloads/Gold_SA1.csv") ## due to weird math shit going on

## rental stress
Gold_SA1 <- read.csv("C:/Users/Julius/Downloads/Gold_SA1.csv")
Gold_SA1 <- as.data.frame(Gold_SA1)
Gold_SA1$rental_stress <- round_any(Gold_SA1$Median_rent_weekly/Gold_SA1$Median_tot_hhd_inc_weekly,0.02)
Gold_SA1$Median.weekly.household.income.... <- round_any(Gold_SA1$Median_tot_hhd_inc_weekly,100)

## rounding job class / age 
tot_working <- (Gold_SA1$white_collar + Gold_SA1$blue_collar + Gold_SA1$Managers)
Gold_SA1$white_collar <- round(Gold_SA1$white_collar/tot_working,1)
Gold_SA1$blue_collar <- round(Gold_SA1$blue_collar/tot_working,1)
Gold_SA1$Managers <- round(Gold_SA1$Managers/tot_working,1)

tot_pop <- Gold_SA1$X0.to.17.years.old + Gold_SA1$X18.to.34.years.old + Gold_SA1$X35.to.49.years.old + Gold_SA1$X50.to.64.years.old + Gold_SA1$X65.to.79.years.old + Gold_SA1$X80.years.old.and.over
Gold_SA1$X0.to.17.years.old <- round(Gold_SA1$X0.to.17.years.old/tot_pop, 2)
Gold_SA1$X18.to.34.years.old <- round(Gold_SA1$X18.to.34.years.old/tot_pop, 2)
Gold_SA1$X35.to.49.years.old <- round(Gold_SA1$X35.to.49.years.old/tot_pop, 2)
Gold_SA1$X50.to.64.years.old <- round(Gold_SA1$X50.to.64.years.old/tot_pop, 2)
Gold_SA1$X65.to.79.years.old <- round(Gold_SA1$X65.to.79.years.old/tot_pop, 2)
Gold_SA1$X80.years.old.and.over <- round(Gold_SA1$X80.years.old.and.over/tot_pop, 2)

Gold_SA1$Born.overseas <- round(Gold_SA1$Born.overseas/tot_pop, 2)

Gold_SA1 <- Gold_SA1[-1,]

Gold_SA1$Managers[Gold_SA1$Managers == 0.3] <- 0.2
Gold_SA1$Median.weekly.household.income....[Gold_SA1$Median.weekly.household.income.... == 2300] <- 2350
Gold_SA1$Median.weekly.household.income....[Gold_SA1$Median.weekly.household.income.... == 2200] <- 2250
Gold_SA1$Median.weekly.household.income....[Gold_SA1$Median.weekly.household.income....>2400] <- 2400
Gold_SA1$Median.weekly.household.income....[Gold_SA1$Median.weekly.household.income....<950] <- 950
Gold_SA1$blue_collar[Gold_SA1$blue_collar < 0.2 ] <- 0.2
Gold_SA1$white_collar[Gold_SA1$white_collar > 0.6 ] <- 0.6
Gold_SA1$Managers[Gold_SA1$Managers > 0.2 ] <- 0.2
Gold_SA1$rental_stress[Gold_SA1$rental_stress == 0.14] <- 0.12
Gold_SA1$rental_stress[Gold_SA1$rental_stress == 0.08] <- 0.06
Gold_SA1$rental_stress[Gold_SA1$rental_stress < 0.06] <- 0.06
Gold_SA1$rental_stress[Gold_SA1$rental_stres > 0.32] <- 0.32
Gold_SA1$rental_stress[Gold_SA1$rental_stress == 0.1] <- 0.06
Gold_SA1$Born.overseas[Gold_SA1$Born.overseas == 0.45] <- 0.44
Gold_SA1$Born.overseas[Gold_SA1$Born.overseas == 0.47] <- 0.46
Gold_SA1$Born.overseas[Gold_SA1$Born.overseas > 0.54] <- 0.54
## filler dataframe 
state_df <- data.frame(electorate = rep(-1, 338))

## generating new data for the data frame
Gold_SA1 <- rownames_to_column(Gold_SA1)
for(i in 2:length(levels(as.factor(Gold_SA1$rowname)))) {
  poststrat_state <- Gold_SA1[Gold_SA1$rowname == i, ]
    posterior_prob_state <- posterior_linpred(
    fit,
    transform = TRUE,
    draws = 4000,
    newdata = as.data.frame(poststrat_state)
  )
poststrat_prob_state <- posterior_prob_state # %*% (census_tmp$Tot_P_P) / sum(census_tmp$Tot_P_P)
  #This is the estimate for popn in state:
  state_df$model_state_sd[i] <- round(sd(poststrat_prob_state), 6)
  state_df$model_state_swing[i] <- round(mean(poststrat_prob_state), 6)
  state_df$SA1 <- Gold_SA1$SA1_7DIGITCODE_2016
  }
```
